Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-15 longoutput.tex
Make theorem statements

@@

The transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
We modify the circuit as appropriate to obtain $C'$ that has size $T'\leq 4T$. We prove a theorem about this circuit that we'll use later.

@@

Let $C$ undergo the above transformations so it has the following properties
\begin{itemize}
	\item All states are real (including initial, intermediate states, and output).
	\item Consists of only Hadamard and Toffoli gates
	\item The last $\gamma$ of the gates are all identity gates (easily achievable by padding)
\end{itemize}

@@

Let $C$ be a circuit with the above properties. Define the following quantities.
\begin{itemize}
	\item $C=U_T\ldots U_1$
	\item Let $x$ be the circuit input. Which is classical.
	\item Let $y$ denote the initial state. That is, $x$ possibly concatenated with ancillaries.
	\item Let $y_i$ denote the $i$-th bit of $y$
	\item Let $n$ be the number of qubits in $C$
\end{itemize}

@@

Now we consider the kernels of the Hamiltonians we defined. Notice the following.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$
$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
We now consider the space outside the desired state.
$$S=(\spn\set{\psi_{circuit}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$ to obtain the following properties.
\begin{itemize}
	\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
	\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$. There are $O(T)$ nonzero components, whose coefficients are each at most $O(T^3)$.
\end{itemize}

>>>>

Here we construct a transform that we will use to... TODO Editorial intro.

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
		\item uses $n$ qubit, including ancillaries.
	\end{itemize}
	Then a classical machine, given $C$ and some classical $x$, can compute a circuit $C'$ and a classical string $x'$ that:
	\begin{itemize}
		\item $C'$ consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
		\item $C'$ uses $n+1$ qubits.
		\item All states are real (including initial, intermediate states, and output).
		\item The measurement results of $C(x)$ and the first $n$ qubits of $C'(x')$ are identically distributed.
	\end{itemize}
\end{theorem}

\begin{proof}

@@

The transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
\end{proof}

Now we also prove a theorem about the circuit after transformation that we'll use later.

@@

@@

Here we reduce a circuit into a local Hamiltonian instance with a few additional properties as below.

\begin{theorem}
	Let $C$ be a circuit such that:
	\begin{itemize}
		\item $C=U_T\ldots U_1$, where $U_i$ are either $H$ or $\Lambda^2(X)$
	\end{itemize}
	Let $x$ be a classical string. Then a classical machine can construct in polynomial time a local Hamiltonian instance such that:
	\begin{itemize}
		\item its ground state is $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$ where $y$ is $x$ possibly concatenated with ancillaries.
		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
		\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

\begin{proof}

Let $C$ be a circuit with the above properties. Define the following quantities.
\begin{itemize}
	\item Let $y$ denote the initial state. That is, $x$ possibly concatenated with ancillaries.
	\item Let $y_i$ denote the $i$-th bit of $y$
	\item Let $n$ be the number of qubits in $C$
\end{itemize}

@@

Now we consider the kernels of the Hamiltonians we defined. Notice the following.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$
$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
We now consider the space outside the desired state.
$$S=(\spn\set{\psi_{circuit}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
\end{proof}
